---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

[![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)](https://github.com/joethorley/stability-badges#experimental)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/mcmcdata.svg?branch=master)](https://travis-ci.org/poissonconsulting/mcmcdata)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/mcmcdata?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/mcmcdata)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/mcmcdata/master.svg)](https://codecov.io/github/poissonconsulting/mcmcdata?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# mcmcdata

## Introduction

`mcmcdata` is an R package to manipulate Monte Carlo Markov Chain samples and data.

## Installation

To install the latest version from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/mcmcdata")
```

## Demonstration
```{r}
library(mcmcdata)

print(mcmc_data_example)

md_ex <- slice(mcmc_data_example, c(1,2,2))
print(md_ex)
md_ex <- group_by(md_ex, homeworld, species)
coef(summarise(md_ex))
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "mcmcdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/mcmcdata/issues).

[Pull requests](https://github.com/poissonconsulting/mcmcdata/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms

## Inspiration

- coda and rjags
