---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/mcmcdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/mcmcdata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/mcmcdata/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/mcmcdata?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

# mcmcdata

## Introduction

`mcmcdata` is an R package to manipulate Monte Carlo Markov Chain samples and data.

## Installation

To install the latest version from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/mcmcdata")
```

## Demonstration
```{r}
library(mcmcdata)

print(mcmc_data_example)

md_ex <- slice(mcmc_data_example, c(1,2,2))
print(md_ex)
md_ex <- group_by(md_ex, homeworld, species)
coef(summarise(md_ex))
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "mcmcdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/mcmcdata/issues).

[Pull requests](https://github.com/poissonconsulting/mcmcdata/pulls) are always welcome.

## Code of Conduct

Please note that the mcmcdata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Inspiration

- coda and rjags
